### 2022-03-12 ch1.tex
Finish copyediting ch 1

This dissertation focuses on how people search for information and how people
rely on this information and to inform their health-behaviors and develop social
norms. Information permeates every facet of human society, from the hordes of
data gathered through digital trace data or the passing gossip between friends.
Human communication and human society are based on the circulation of
information and knowledge. Information can be shared and promoted by others
through information campaigns and consumed by an individual, called information
push, or intentionally sought out by individuals, called information pull
\citep{cybenkoFoundationsInformationPush1999}.

We must understand the information individuals receive and seek out in order
to develop a well functioning society. The information that
one consumes consolidates to create the entire worldview of every individual,
leading to how they understand the world and behave civilly therein. New and
emerging social norms must align with one's worldview to anticipate any sort of 
behavioral change, for better or for worse.

The importance of reputable information and misinformation was clearly evident
in the recent and ongoing Covid-19 pandemic. While the vaccines against the
Covid-19 virus prevent severe illness, hospitalization, and death, only 60\% of
Arizonans over 12 years old are fully vaccinated against the virus. We know that
people exposed to misinformation are much less likely to receive vaccinations
against the virus \citep{loombaMeasuringImpactCOVID192021}. It is not an
exaggeration to claim that misinformation has been deadly for Arizona
\citep{pathakInfodemicsCOVID19Role2020, greene_murphy21}.

This dissertation on information search and norm development provides clear and
timely social implications for Arizona and the United States. This dissertation
uncovers how norms are created during periods of norm uncertainty and builds the
foundation to theorize and test interventions that promote positive norms in
times of disasters and uncertainty. Specifically, I investigate how local
diffusion leads to social norms through information search which will have
strong implications for the prevention of global polarization and the spread of
misinformation.

In academia and policy, the main focus in research on information has always
been the information that is sent to consumers, seeing people as passive
receivers of information. My dissertation instead focuses on individuals as
active agents in their search for information which helps me uncover the
information individuals are exposed to. By looking at how individuals search, I
aim to identify pain points and focus areas for future interventions in the
misinformation process.

@@

\subsection{Information Flow}
% TODO what happened before this point? 
A critical turning point in the study of the flow information was put forth by
renowned Sociologist Paul Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}.
Lazarsfeld and others theorized that the media did not directly influence the
masses, but that a "Two-Step Flow" was occurring where "opinion leaders"
interpreted messages from mass media and then, in turn, promoted their opinions
to the masses \citep{katzPersonalInfluencePart1955}. The opinion leaders
interpret, explain, and diffuse contents to "opinion followers". From a networks
perspective, "people rarely act on mass-media information unless it is also
transmitted through personal ties" \citep[p. 1374]{granovetterStrengthWeakTies1973}. 
Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}'s first study focused on
politics but follow up studies from \citep{katzPersonalInfluencePart1955} showed
that this model matched information flows beyond the political realm. In
contrast to the one-step flow, where media directly influences the masses,
Lazarsfeld's theory remains in prominence today. While many scholars assumed
that modern micro-targeted marketing strategies would provide evidence for a
one-step flow perspective \citep{bennettOneStepFlowCommunication2006}, many
scholars find that "opinion leaders" (often influencers and celebrities) still
create a two-step flow of information transmission \citep{choi15,
hilbertOneStepTwo2017}.

The spread of information has been thoroughly studied from the prospective
of social networks. Individuals engage with each other and their distributive
ties to create community contexts where norms, beliefs, and values circulate.
Information diffuses through communities and social networks
\citep{fowler2010cooperative, bond_etal12, klarEffectNetworkStructure2017}.
However, "different things spread in different ways and to different extents"
\citep[p. 563]{christakisSocialContagionTheory2013} and information can spread
differently than a virus or behavior. Important studies in the spread of
information through networks include the study of adoption of innovations by
physicians \citep{colemanDiffusionInnovationPhysicians1957}, how new inventions
are adopted from early adopters to laggards
\citep{rogersDiffusionInnovations1962}, how weak ties help bind networks and
diffuse information \citep{granovetterStrengthWeakTies1973}, how social ties
spread information about job opportunities
\citep{granovetterGettingJobStudy1995, montgomeryJobSearchNetwork1992}, how
information spreads best when weak and strong ties are balanced (embeddedness)
\citep{uzziSocialStructureCompetition1997}, and more recent innovations in the
stickiness of complex contagion \citep{centolaComplexContagionsWeakness2007}.

\subsection{Information Search}
I only discussed the way that information is passively
consumed through push efforts by opinion leaders and social networks. However,
sociological literature is really sparse on the opposite behavior: active
directed searching by individuals to obtain information.
\citep{pejtersenDesignComputeraidedUsersystem1984}, a scholar of library and
information science, theorized that there are 5 strategies for searching for
information. The most common strategy is browsing, where people follow leads
based on associations without planning ahead. Another strategy is analytical,
which includes an explicit consideration of all facets of the question to guide
a search. The empirical method guides the search based on tactics that were
successful in past research. The known site strategy is to go to the direct
source of the information if known. And finally, the similarity method is to
find information based on another similar question that already has an answer.
These 5 strategies vary in their demands for prior knowledge, cognitive
processing, memory, and time spent. While this theory is aimed at finding
information in a library setting, scholars have extended the theory to other
fields and validated the framework \citep{fidelHumanInformationInteraction2012};
the frame is a useful beginning point for the theories of information search
through network activation or through computer-mediated communication.

@@

The introduction of the internet and digital technologies introduced an epochal
disruption in the communication and informational-search mediums that people had
available to them. Computer-mediated communication was the largest communication
revolution in a century, changing the speed and availability of communication
between individuals by electronic mail, instant messaging, two-way interactive
video calls, discussion forums, blogs, and social networking
\citep{rainie2012networked}. Computer-mediated communication encompasses any
sort of communication through computers connected to the internet; the umbrella
term involves both synchronous and asynchronous communication as well as
one-to-one, one-to-many, or many-to-many exchanges. Social media, on the other
hand, are more specific, and are "Internet-based, disentrained, and persistent
channels of mass personal communication facilitating perceptions of interactions
among users, deriving value primarily from user-generated content.” \citep[][p.
50]{carr2015social}. While an email between colleagues is computer-mediated
communication, it is not social media as there is only one interaction between
users and there is no value derived from the user-generated content outside the
pair \citep{bayer_etal20}. Even more restrictive still is the social networking
site, which consists of a profile, a network, and a stream or a feed
\citep{boyd2007social, ellison2013sociality,},  often also involving a messaging
component  \citep{bayer_etal20}. Social networking sites are also interesting
because they often uniquely combine one-to-one communication within the context
of one-to-many communication, like resharing a television news story to your
facebook feed and chatting with others about the content in the comments
section. But what do these classifications mean for the information-seeking
behaviors of individuals in the 21st century? Not only is it quicker to perform
network activation and seek support, but people are "permanently online,
permanently connected" making activation easy \citep{vorderer2017permanently}.
The constant connectedness facilitates communication, but also presents people
with overchoice, or the difficulty in making a decision because simply every
network connection you may want to activate is permanently connected and easy to
reach. In other words, constant connection may be debilitating to many who are
seeking information. \citet{smallSomeoneTalk2017} provides many examples of this
when he demonstrates that more often than not, graduate students who needed
support simply asked "miscellaneous classmates encountered down the hall" (p.
176) rather than their trusted, long-term confidants. It seems that network
activation may rely on more than just trust; namely: convenience.

The digital age did not only revolutionize communication. It also
revoluitionized information search \citep{ramirez2002information}. Just as prior
to the digital age you could open an encyclopedia or peruse the library to find
the information you seek, much of the computer-mediated information search
surely occurs outside of social network activation contexts. While searching in
an encyclopedia is far less common today, internet search engines have
revolutionizes the speed and ease at which we can find information. Early web
search engines allowed information seekers to browse web directories and early
engines like Yahoo! and Altavista found success using keyword-based search,
though the early algorithms were limited in what they could find and relied
heavily on the wording of the queries. Google, the major web search engine used
today, introduced the disrputive PageRank algorithm in the early 2000s, securing
its place as the information hegemon of the 21st century
\citep{brin1998anatomy}. Not only has computer-mediated information search
revolutionized the ease of obtaining information, but it has also changed out
brains. \citet{sparrow2011google} show that the digital age has led to worse
memory and higher reliance on technology to keep track of information for us.
These search engines have also shaped our cultures by controlling, whether
through algorithm or intentionally, the information the engine provides. For
example, Google will not show results for various neo-Nazi websies in countries
where holocaust denial is illegal, like France and Germany. This is illustrative
of the control engines have over information and how this control may introduce
various political, economic, and social biases in the information they provide
\citep{segev2010google}. When 99Firms \citeyearpar{99firms22} compiled the data
from sources like NetMarketShare, Statista, DuckDuckGo, Yahoo Finance, Google,
and Pew Research they found that about about Around 93\% of all web traffic is
via a search engine and that 78.39\% of all internet search use Google. Because
computer-mediated information search is instantaneous and only requires mobile
data or wifi, there is virtually no cost to seeking information on one of these
mediums.

@@

One way to find information is to activate network ties to find out information
through a form of social support. Social support, while previously used
interchangeably with the term social networks and social integration
\citep{houseStructuresProcessesSocial1988}, are the emotional, informational,
and instrumental assistance functions performed between social ties and have
strong and measurable association with health outcomes
\citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}.
Informational support is the process of seeking "help in defining,
understanding, and coping with problematic events and include education, advice,
or referral to another source of support" \citep[p. 640]{winemiller_etal93}.
Brashers, a health communications researcher, defines informational support
slightly differently, focusing on the exchange of information that "facilitates
coping with life stresses... that may be exchanged among members of a support
network" \citeyearpar[p. 260]{brashersInformationSeekingAvoiding2002}. Both of
these definitions provide important lenses for my question of how
computer-mediated or interpersonal information-seeking strategies vary. 
Some research has revealed that Facebook users who utilize the platform to 
find information and to maintain relationships have high levels of bridging
social capital \citep{liu2016meta}. However, this leaves the question 
of who activates their social networks for information using social networking 
sites like Facebook over activating these networks in face-to-face interactions.

@@

There has been some research into how different platforms allow for different user 
experiences or "affordances" \citep{boyd2010social}. For example, \citet{bossetta18} first show
that all social media platforms must provide "tools that are easy to use and 
functional to the demands of varying using demographics" (p. 473). They also
explain how each digital architecture enables, contstrains and shapes how users
behave on their platform and in virtual space, leading to many different experiences 
along the dimensions of searchability, connectivity, and privacy.

@@

\subsection{Social Norms}
I showed the levels of uncertainty may direct how and when people
search for information. However, in situations of rapidly changing norms,
uncertainty is prevalent. This dissertation will also focus on developing
new social norms in situations of uncertainty about how to behave. 
Minimal research exists in quickly emerging
norms in times of emergency, but shows that people likely to rely on the
behavior of others' to set their own norms for behavior \citep{alvarez2018,
horneNormsIntegratedFramework2020}. This project will investigate how search
contributes to the development of said spontaneous norms.

@@

The causes and logics of social norms are debated. The consequentialist
argument for norms focuses merely on the consequence a behavior has on
group members and that norms will be promoted if the behavior benefits
others and denounced if it negatively affects others \citep{ullmannmargalitEmergenceNorms1977}.
 While this theory has been tested and performs well in the lab,
researchers have raised questions regarding its ecological validity
\citep{horneNormsIntegratedFramework2020}. One of the main critiques of the
consequentialist argument is that it relies on the same interpretation of the perceived action
by all parties of what is harmful and beneficial. The Relational argument 
for norms is based on the value people place on their relationships and
the assumption that people will behave in ways that will garner them
positive social reactions. This argument relies on individuals assuming
what their peers will approve and disapprove of. In turn, norms are
developed when individuals make inferences from their social worlds
\citep{fryeCulturalMeaningsAggregation2017}.

Importantly, people look to others performing an action and often
interpret that performance as an indication that an action is approved,
paying particular attention to high-status individuals and institutions
\citep{robalinoPeerEffectsAdolescent2018, tankardEffectSupremeCourt2017}.

@@

\citet{goldbergSocialContagionAssociative2018} argue that the state of the
literature on diffusion and social contagion, discussed above, is erroneous.
They propose an important linkage that had been missed in previous research of
the diffusion of behavior (or, as I interpret it, the creation of new norms).
They argue that what actually diffuses during social contagion are the
perceptions about which beliefs or behaviors are compatible with one another,
what they call "associative diffusion". 
This relates back to the theory of relational norms, where individuals assume
what their peers will approve and disapprove of. In order for these assumptions 
to take place, they must have an understanding of which behaviors and beliefs
are possessed by whom in their network and how new associations may influence
or disrupt the expected actions. In times of behavioral uncertainty, I
theorize that individuals strategically look towards other high-status
individuals, institutions, and perform regimented searches to establish for
themselves the behavior that is compatible with other cognitive biases they
hold.

@@

This dissertation uses three articles to investigate different parts of
the aforementioned theoretical framework (figure \ref{fig:concept-map}).
The dissertation is divided into three parts, with Article 1 focusing 
on online information search, Article 2 focusing on online and offline
information search, and Article 3 investigating the entire information
push and pull process in the context of establishing new norms.

@@

I fail to find correlation among any of the Google Trends tested and their
validated indicators. While some Google Trends tested were significantly
associated with the outcome in the regression models, effects tended to be small
and the total model interpretability remained low, even when controlling for
demographic variables. This article shows that there is no external validity of
Google Trends for these uses and social scientists will find no replacement for
high quality survey data with Google Trends.

@@

Knowing that Google trends data only encompasses a small portion of the
information-seeking done by modern humans, it is important to
investigate what leads individuals to search for a question online using
a search engine (contributing to macro-level trends data) versus more
traditional means of information gathering, such as network activation
(asking someone in their social network for informational support). 
Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline. Using theories of social
support and uses and gratifications theory, I investigate the factors associated
with each vehicle type when on information seeking vehicle: personal connection,
doctor, social networking site, online forum, and online search engine. I use
original survey data of 948 Americans to investigate their experiences seeking out
information about the Covid-19 vaccines.

@@

In this article, I find little evidence that online search is more utilized than
seeking social support from personal network connections or health professionals
as I hypothesize based on uses and gratifications theory. I find evidence that
the categorizations of vehicles queried in this survey are indeed conceptually
different from each other and that the utilization of different vehicles varies
by demography and information exposure points. Finally, I find that different
exposure points and information search vehicles hold real world consequences
through their associations with Covid-19 vaccination rates and intentions, as
information from a doctor increased the Covid-19 vaccination uptake while
receiving information from a Social Networking Site like Facebook or Twitter was
associated with lower odds of vaccination.

@@

These models show that complex contagion is a valid 
framework for the social contagion of new norms during Covid-19. Importantly, I find
important moderating effect of signal discordance, the contextual diversity of
signals received by an ego. This paper shows that the contagion process is not
fully understood without looking at the context of each exposure point within the
range of exposures one experiences.

@@

% search as an agentic process
This research will make contributions to multiple subfields and literatures. 
First and foremost, these articles make a contribution to the sociological literature.
The spread of information has long been investigated in the discipline (diffusion, mass
communication, social influence). However, it is almost always researched from a structural
perspective which disregards individual agency and choice in the
acquisition of new information. This dissertation adopts the second perspective,
centering people as active agents in their search for information algined
with their own preferences and gratifications instead of just
passive receivers of information signals.
Taking this agentic perspective is critical in the study of information
diffusion when combined with cognitive perspectives like that of
Goldberg and Stein (2018). How people search for information determines
the information that they find. The information they uncover is filtered
through cognitive biases and predispositions to how they interpret and
act upon the newfound information. Searching for informational support
through social network ties theoretically will uncover potentially
different information than that would be uncovered through online web
search and will change how people are organized and how people behave.
\hyperlink{paper-2}{Article 2} importantly shows that 
the vehicles uses to search for information have a significant impact on the choice to get vaccinated against Covid-19, a real-world consequence to the minutiae of individual information search.

% CSS & big data
This dissertation also contributes to computational social science \&
critical big data studies. I base much of my dissertation around Google
Search Trends, which are relatively underutilized in the social sciences
compared to health sciences and business. Because \hyperlink{paper-1}{Article 1} 
takes a critical big data studies approach, I take into account the potential
pitfalls with any source of big data \citep{mcfarlandBigDataDanger2015} and explicitly
test just how well Google Trends can be used as an indicator for different concepts. 
Importantly, I find that there is no replacement for high quality survey data with Google Trends. 
This is a large contribution to the field of critical big data studies but also provides
the groundwork for future tests of external validity for big data for future computational
social scientists.

@@

% social norms
Additionally, this dissertation investigates how social norms are
formed in situations of uncertainty, an area that is far less developed in
sociology. While sociologists have studied social norms since the
formation of the discipline, norms are most often studied under the lens
of the emergence of norms and transmission of norms between groups, 
deviance and social control, the interaction of norms as "mental representations of appropriate behavior" \citep{aarts2003silence}, and research categorizing different types of norms (e.g. descriptive versus injunctive, prescriptive versus proscriptive).  
The focus on the formation of new social norms during times of upheaval 
has implications for interventions in social behavioral outcomes, 
research on cultural change, and the spread of cognitive associations. 
Moreover, \hyperlink{paper-3}{Article 3} focuses on how how conflicting
behaviors become settled into cognitive associations, providing
a relevant framework for research on unrest and disasters.

>>>>

This dissertation focuses on how people search for information and how people
rely on this information to inform their health-behaviors and develop social
norms. Information permeates every facet of human society, from the hordes of
data gathered through digital-trace data or the passing gossip between friends.
Human communication and human society are based on the circulation of
information and knowledge. Information can be shared and promoted by others
through information campaigns and consumed by an individual, called information
push, or information can be intentionally sought out by individuals, 
called information pull \citep{cybenkoFoundationsInformationPush1999}.

We must understand the information individuals receive and seek out 
to develop a well-functioning society. The information that
one consumes consolidates to create the entire worldview of every individual,
leading to how they understand the world and behave civilly therein. New and
emerging social norms must align with one's worldview to anticipate any sort of 
behavioral change, for better or for worse.

The importance of reputable information and misinformation was clear
in the recent and ongoing Covid-19 pandemic. While the vaccines against the
Covid-19 virus prevent severe illness, hospitalization, and death, only 60\% of
Arizonans over 12 years old are fully vaccinated against the virus. We know that
people exposed to misinformation are much less likely to receive vaccinations
against the virus \citep{loombaMeasuringImpactCOVID192021}. It is not an
exaggeration to claim that misinformation has been deadly for Arizona
\citep{pathakInfodemicsCOVID19Role2020, greene_murphy21}.

This dissertation on information search and norm development provides clear and
timely social implications for Arizona and the United States. I
uncovers how norms are created during periods of norm uncertainty and builds the
foundation to theorize and test interventions that promote positive norms in
times of disasters and uncertainty. Specifically, I investigate how local
diffusion leads to social norms through information search which will have
strong implications for the prevention of global polarization and the spread of
misinformation.

In academia and policy, the focus in research on information has always
been the information that is sent to consumers, seeing people as passive
receivers of information. My dissertation instead focuses on individuals as
active agents in their search for information. By looking at how individuals 
search, I aim to identify pain points and focus areas for future interventions
in the misinformation process.

@@

\subsection{Information Flow}
Humans have long been interested in how to persuade the masses. With the 
rise of democracy, the need of the powerful to persuade and appease the
masses dramatically increased. And for a while, behavioral scientists 
adopted really simplistic models of persuasion like the hypodermic needle model
\citep{bineham1988historical}. This simplistic perception of human behavior 
thought that the media basically injects messages into passive consumers
who wholly accept the message and are affected by its contents \citep{lasswellpropaganda}.

A critical turning point in the study of the flow of information was put forth by
renowned Sociologist Paul Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}.
Lazarsfeld and others theorized that the media did not directly influence the
masses, but that a "Two-Step Flow" was occurring where "opinion leaders"
interpreted messages from mass media and then, in turn, promoted their opinions
to the masses \citep{katzPersonalInfluencePart1955}. The opinion leaders
interpret, explain, and diffuse contents to "opinion followers". From a networks
perspective, "people rarely act on mass-media information unless it is also
transmitted through personal ties" \citep[p. 1374]{granovetterStrengthWeakTies1973}. 
Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}'s first study focused on
politics but follow up studies from \citep{katzPersonalInfluencePart1955} showed
that this model matched information flows beyond the political realm. In
contrast to the one-step flow, where media directly influences the masses,
Lazarsfeld's theory remains in prominence today. While many scholars assumed
that modern micro-targeted marketing strategies would provide evidence for a
one-step flow perspective \citep{bennettOneStepFlowCommunication2006}, many
scholars find that "opinion leaders" (often influencers and celebrities) still
create a two-step flow of information transmission \citep{choi15,
hilbertOneStepTwo2017}.

The spread of information has been thoroughly studied from the perspective
of social networks. Individuals engage with each other and their distributive
ties to create community contexts where norms, beliefs, and values circulate.
Information diffuses through communities and social networks
\citep{fowler2010cooperative, bond_etal12, klarEffectNetworkStructure2017}.
However, "different things spread in different ways and to different extents"
\citep[p. 563]{christakisSocialContagionTheory2013} and information can spread
differently than a virus or behavior. Important studies in the spread of
information through networks include the study of adoption of innovations by
physicians \citep{colemanDiffusionInnovationPhysicians1957}, how new inventions
are adopted from early adopters to laggards
\citep{rogersDiffusionInnovations1962}, how weak ties help bind networks and
diffuse information \citep{granovetterStrengthWeakTies1973}, how social ties
spread information about job opportunities
\citep{granovetterGettingJobStudy1995, montgomeryJobSearchNetwork1992}, how
information spreads best when weak and strong ties are balanced (embeddedness)
\citep{uzziSocialStructureCompetition1997}, and more recent innovations in the
stickiness of complex contagion \citep{centolaComplexContagionsWeakness2007}.

\subsection{Information Search}
I have only discussed the way that information is passively
consumed through push efforts by opinion leaders and social networks. However,
sociological literature is sparse on the opposite behavior: active
directed searching by individuals to obtain information.
\citep{pejtersenDesignComputeraidedUsersystem1984}, a scholar of library and
information science, theorized that there are 5 strategies for searching for
information. The most common strategy is browsing, where people follow leads
based on associations without planning. Another strategy is analytical,
which includes an explicit consideration of all facets of the question to guide
a search. The empirical method guides the search based on tactics that were
successful in past research. The known site strategy is to go to the direct
source of the information if known. And finally, the similarity method is to
find information based on another similar question that already has an answer.
These 5 strategies vary in their demands for prior knowledge, cognitive
processing, memory, and time spent. While this theory is aimed at finding
information in a library setting, scholars have extended the theory to other
fields and validated the framework \citep{fidelHumanInformationInteraction2012};
the frame is a useful beginning point for the theories of information search
through network activation or through computer-mediated communication.

@@

The introduction of the internet and digital technologies introduced an epochal
disruption in the communication and informational-search mediums that people had
available to them. Computer-mediated communication was the largest communication
revolution in a century, changing the speed and availability of communication
between individuals by electronic mail, instant messaging, two-way interactive
video calls, discussion forums, blogs, and social networking
\citep{rainie2012networked}. Computer-mediated communication encompasses any
sort of communication through computers connected to the internet; the umbrella
term involves both synchronous and asynchronous communication as well as
one-to-one, one-to-many, or many-to-many exchanges. Social media, on the other
hand, are more specific, and are "Internet-based, disentrained, and persistent
channels of mass personal communication facilitating perceptions of interactions
among users, deriving value primarily from user-generated content.” \citep[][p.
50]{carr2015social}. While an email between colleagues is computer-mediated
communication, it is not social media as there is only one interaction between
users and there is no value derived from the user-generated content outside the
pair \citep{bayer_etal20}. Even more restrictive still is the social networking
site, which consists of a profile, a network, and a stream or a feed
\citep{boyd2007social, ellison2013sociality},  often also involving a messaging
component  \citep{bayer_etal20}. Social networking sites are also interesting
because they often uniquely combine one-to-one communication within the context
of one-to-many communication, like resharing a television news story to your
Facebook feed and chatting with others about the content in the comments
section. But what do these classifications mean for the information-seeking
behaviors of individuals in the 21st century? Not only is it quicker to perform
network activation and seek support, but people are "permanently online,
permanently connected" making activation easy \citep{vorderer2017permanently}.
The constant connectedness facilitates communication, but also presents people
with overchoice, or the difficulty in deciding because simply every
network connection you may want to activate is permanently connected and easy to
reach. In other words, constant connection may be debilitating to many who are
seeking information. \citet{smallSomeoneTalk2017} provides many examples of this
when he demonstrates that often, graduate students who needed
support simply asked "miscellaneous classmates encountered down the hall" (p.
176) rather than their trusted, long-term confidants. It seems that network
activation may rely on more than just trust; namely: convenience.

The digital age did not only revolutionize communication. It also
revolutionized information search \citep{ramirez2002information}. Just as prior
to the digital age you could open an encyclopedia or peruse the library to find
the information you seek, much of the computer-mediated information search
surely occurs outside of social network activation contexts. While searching in
an encyclopedia is far less common today, internet search engines have
revolutionized the speed and ease at which we can find information. Early web
search engines allowed information seekers to browse web directories and early
engines like Yahoo! and Altavista found success using keyword-based search,
though the early algorithms were limited in what they could find and relied
heavily on the wording of the queries. Google, the major web search engine used
today, introduced the disruptive PageRank algorithm in the early 2000s, securing
its place as the information hegemon of the 21st century
\citep{brin1998anatomy}. Not only has computer-mediated information search
revolutionized the ease of obtaining information, but it has also changed our
brains. \citet{sparrow2011google} show that the digital age has led to worse
memory and higher reliance on technology to keep track of information for us.
These search engines have also shaped our cultures by controlling, whether
through algorithm or intentionally, the information the engine provides. For
example, Google will not show results for various neo-Nazi websites in countries
where holocaust denial is illegal, like France and Germany. This is illustrative
of the control engines have over information and how this control may introduce
various political, economic, and social biases in the information they provide
\citep{segev2010google}. When 99Firms \citeyearpar{99firms22} compiled the data
from sources like NetMarketShare, Statista, DuckDuckGo, Yahoo Finance, Google,
and Pew Research they found that about Around 93\% of all web traffic is
via a search engine and that 78.39\% of all internet searches performed are done
so using Google. Because computer-mediated information search is instantaneous 
and only requires mobile data or WiFi, there is virtually no cost to seeking
information on one of these mediums.

@@

One way to find information is to activate network ties to find out information
through a form of social support. Social support, while previously used
interchangeably with the term social networks and social integration
\citep{houseStructuresProcessesSocial1988}, are the emotional, informational,
and instrumental assistance functions performed between social ties and have
strong and measurable association with health outcomes
\citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}.
Informational support is the process of seeking "help in defining,
understanding, and coping with problematic events and include education, advice,
or referral to another source of support" \citep[p. 640]{winemiller_etal93}.
Brashers, a health communications researcher, defines informational support
slightly differently, focusing on the exchange of information that "facilitates
coping with life stresses... that may be exchanged among members of a support
network" \citeyearpar[p. 260]{brashersInformationSeekingAvoiding2002}. Both
definitions provide important lenses for my question of how
computer-mediated or interpersonal information-seeking strategies vary. 
Some research has revealed that Facebook users who utilize the platform to 
find information and to maintain relationships have high levels of bridging
social capital \citep{liu2016meta}. However, this leaves the question 
of who activates their social networks for information using social networking 
sites like Facebook instead of activating these networks in face-to-face
interactions.

@@

There has been some research into how different platforms allow for different user 
experiences or "affordances" \citep{boyd2010social}. For example, \citet{bossetta18} first show
that all social media platforms must provide "tools that are easy to use and 
functional to the demands of varying user demographics" (p. 473). They also
explain how each digital architecture enables, constrains and shapes how users
behave on their platform and in virtual space, leading to many different experiences 
along the dimensions of searchability, connectivity, and privacy.

@@

\subsection{Social Norms}
I showed that the levels of uncertainty may direct how and when people
search for information. However, in situations of rapidly changing norms,
uncertainty is prevalent. This dissertation will also focus on developing
new social norms in situations of uncertainty about how to behave. 
Minimal research exists in quickly emerging
norms in times of emergency but shows that people are likely to rely on the
behavior of others to set their own norms for behavior \citep{alvarez2018,
horneNormsIntegratedFramework2020}. This project will investigate how search
contributes to the development of said spontaneous norms.

@@

The causes and logics of social norms are debated. The consequentialist
argument for norms focuses merely on the consequence a behavior has on
group members and that norms will be promoted if the behavior benefits
others and denounced if it negatively affects others \citep{ullmannmargalitEmergenceNorms1977}.
 While this theory has been tested and performs well in the lab,
researchers have raised questions regarding its ecological validity
\citep{horneNormsIntegratedFramework2020}. One of the main critiques of the
consequentialist argument is that it relies on the same interpretation of the perceived action
by all parties of what is harmful and beneficial. The Relational argument 
for norms is based on the value people place on their relationships and
the assumption that people will behave in ways that will garner them
positive social reactions. This argument relies on individuals assuming
what their peers will approve and disapprove of. In turn, norms are
developed when individuals make inferences from their social worlds
\citep{fryeCulturalMeaningsAggregation2017}. Importantly,
people look to others performing an action and often
interpret that performance as an indication that an action is approved,
paying particular attention to high-status individuals and institutions
\citep{robalinoPeerEffectsAdolescent2018, tankardEffectSupremeCourt2017}.

@@

\citet{goldbergSocialContagionAssociative2018} argue that the state of the
literature on diffusion and social contagion, discussed above, is erroneous.
They propose an important linkage that had been missed in previous research of
the diffusion of behavior (or, as I interpret it, the creation of new norms).
They argue that what actually diffuses during social contagion are the
perceptions about which beliefs or behaviors are compatible with one another,
what they call "associative diffusion". 
This relates back to the theory of relational norms, where individuals assume
what their peers will approve and disapprove of. For these assumptions 
to take place, they must understand which behaviors and beliefs
are possessed by whom in their network and how new associations may influence
or disrupt the expected actions. In times of behavioral uncertainty, I
theorize that individuals strategically look towards other high-status
individuals, institutions, and perform regimented searches to establish for
themselves the behavior that is compatible with other cognitive associations
and biases they hold.

@@

This dissertation uses three articles to investigate different parts of
the theoretical framework (figure \ref{fig:concept-map}).
The dissertation is divided into three parts, with Article 1 focusing 
on online information search, Article 2 focusing on online and offline
information search, and Article 3 investigating the entire information
push and pull process in the context of establishing new norms.

@@

I fail to find correlation among any of the Google Trends tested and their
validated indicators. While some Google Trends tested were significantly
associated with the outcome in the regression models, effects tended to be small
and the total model interpretability remained low, even when controlling for
demographic variables. This article shows that there is no external validity of
Google Trends for these uses and social scientists will find no replacement for
high quality survey data with Google Trends. Instead, we must only use 
Google Trends to demonstrate interest or attention.

@@

Knowing that Google trends data only encompasses a small portion of the
information-seeking done by modern humans, it is important to
investigate what leads individuals to search for a question online using
a search engine versus more
traditional means of information gathering, such as network activation
(asking someone in their social network for informational support). 
Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline. Using theories of social
support and uses and gratifications theory, I investigate the factors associated
with each information seeking vehicle: personal connection,
doctor, social networking site, online forum, and online search engine. I use
original survey data of 948 Americans to investigate their experiences seeking out
information about the Covid-19 vaccines.

@@

In this article, I find little evidence that online search is more utilized than
seeking social support from personal network connections or health professionals
as I hypothesize based on uses and gratifications theory. I find evidence that
the categorizations of vehicles queried in this survey are indeed conceptually
different from each other and that the utilization of different vehicles varies
by demography and information exposure points. Finally, I find that different
exposure points and information search vehicles hold real world consequences
through their associations with Covid-19 vaccination rates and intentions, as
information from a doctor increases the Covid-19 vaccination uptake while
receiving information from a Social Networking Site like Facebook or Twitter was
associated with lower odds of vaccination.

@@

These models show that complex contagion is a valid 
framework for the social contagion of new norms during Covid-19. Importantly, I find
a novel moderating effect of signal discordance, the contextual diversity of
signals received by an ego. This paper shows that the contagion process is not
fully understood without looking at the context of each exposure point within the
range of exposures one experiences.

@@

% search as an agentic process
This research will make contributions to multiple subfields and literatures. 
First and foremost, these articles contribute to the sociological literature.
The spread of information has long been investigated in the discipline (diffusion, mass
communication, social influence). However, it is almost always researched from a structural
perspective which disregards individual agency and choice in the
acquisition of new information. This dissertation adopts the second perspective,
centering people as active agents in their search for information aligned
with their own preferences and gratifications instead of just
passive receivers of information signals.
Taking this agentic perspective is critical in the study of information
diffusion when combined with cognitive perspectives like that of
Goldberg and Stein (2018). How people search for information determines
the information that they find. The information they uncover is filtered
through cognitive biases and predispositions to how they interpret and
act upon the newfound information. Searching for informational support
through social network ties theoretically will uncover potentially
different information than that would be uncovered through online web
search and will change how people are organized and how people behave.
\hyperlink{paper-2}{Article 2} importantly shows that 
the vehicles used to search for information have a significant impact on the choice to get vaccinated against Covid-19, a real-world consequence to the minutiae of individual information search.

% CSS & big data
This dissertation also contributes to computational social science \&
critical big data studies. I base much of my dissertation around Google
Search Trends, which are relatively underutilized in the social sciences
compared to health sciences and business. Because \hyperlink{paper-1}{Article 1} 
takes a critical big data studies approach, I consider the potential
pitfalls that any source of big data face \citep{mcfarlandBigDataDanger2015} and explicitly
test just how well Google Trends can be used as an indicator for different concepts. 
Importantly, I find that there is no replacement for high quality survey data with Google Trends. 
This is a large contribution to the field of critical big data studies but also provides
the groundwork for future tests of external validity for big data for future computational
social scientists.

@@

% social norms
Additionally, this dissertation investigates how social norms are
formed in situations of uncertainty, an area that is far less developed in
sociology. While sociologists have studied social norms since the
formation of the discipline, norms are most often studied under the lens
of the emergence of norms and transmission of norms between groups, 
deviance and social control, the interaction of norms as "mental 
representations of appropriate behavior" \citep{aarts2003silence}, 
and research categorizing different types of norms (e.g., descriptive 
versus injunctive, prescriptive versus proscriptive).  
The focus on the formation of new social norms during times of upheaval 
has implications for interventions in social behavioral outcomes, 
research on cultural change, and the spread of cognitive associations. 
Moreover, \hyperlink{paper-3}{Article 3} focuses on how conflicting
behaviors become settled into cognitive associations, providing
a relevant framework for research on unrest and disasters.

% social networks / diffusion
This dissertation will also have implications for the study of social
networks and diffusion. \citet{centolaComplexContagionsWeakness2007}
introduced a pivotal disruption to the diffusion literature when
they developed complex contagion, the need for reinforcement through multiple
exposures.  \hyperlink{paper-3}{Article 3} in this dissertation
takes this disruption one step further to demonstrate that the concordance
of the exposure affects the contagion process; in other words, being exposed to a 
diversity of diffusants (discordance) can prevent the diffusant from spreading. 
This critical finding provides many new areas of exploration for scholars 
to further investigate the interdependence between different beliefs that
are diffusing and under what contexts the discordance matters.

% social epidemiology
I also make important contributions to social epidemiology through this
research. Each of the three papers in this dissertation use health case
studies for questions of sociological interest. Because of this, I 
contribute to the social epidemiological conversation on vaccine hesitancy,
health communication, and diffusion of high-risk health behaviors. While
all these areas are important to social epidemiology, there hold
potential important health implications for these contributions on
outside of the academy, covered in the first paragraphs of this chapter.
